### 2016-08-22 ms/ms.tex
changes the perturbation figures, modified the manuscript

We also explored how the robustness to cascading effects changed as
community assembled, using algebraic connectivity--- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic}--- as a proxy for network robustness
(e.g. Gaiarsa et al., submitted). Algebraic connectivity was first
used to describe spectral properties of complex graphs other than
ecological networks, and it is related to how difficult it is to turn
a network into completely disconnected groups of nodes, or species
\citep{fiedler1973algebraic, costa2007characterization}, and also to
flows in . The larger the algebraic connectivity, the more robust a
network is to perturbations (e.g. Gaiarsa et al., submitted).

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/robustness.pdf}
  \caption{The robustness of networks to species extinction and
    perturbation. The robustness to species extinction is measured by
    incrementally removing species by degree, through removing species
    by abundance did not yield qualitatively different results. Points
    are the value for each site at each year of assembly. The solid
    line indicates the mean slope estimate and the dashed lines are
    the $95\%$ confidence intervals around the estimate.}
  \label{fig:rob}
\end{figure}
\clearpage

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not impossible. Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

TRANSITION... Surprisingly, the species that were most variable in
their network position and thus contributed most to network
reorganizations where species with the highest degrees (i.e., most
generalized) and persistence.  For example, the five most ubiquitous
species in our study landscape --- \textit{Halictus ligatus},
\textit{Halictus tripartitus},\textit{Lasioglossum (Dialictus)
  incompletum}, and \textit{Toxomerus marginatus} --- were also the
only species that changed what module (i.e., community) they were
present in across years in all of the assembling hedgerows. Because
species degree and persistence were strongly correlated, it is
difficult to disentangle the causal mechanism for why species with
those characteristics are so variable in their network
position. Generalized species may be best able to exploit the limited
floral resources the intensively managed agriculture landscape, and
thus also most persistent. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a higher degree. Either way, our result suggests
that adaptable species can change their network position to utilize
the most advantageous floral resources, which my depend the other
pollinator species that are present and the state of the floral
resource. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

>>>>

We also explored how the robustness to cascading effects changed as
community assembled, using algebraic connectivity--- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic}--- as a proxy for network robustness
(e.g. Gaiarsa et al., submitted). Algebraic connectivity was first
used to describe spectral properties of complex graphs other than
ecological networks, and it has been extensively studied \citep[e.g.,][]{fiedler1973algebraic, costa2007characterization, mohar1991laplacian, de2007old}.   Algebraic connectivity is related to the mean diameter of a graph and to how difficult it is to turn
a network into completely disconnected groups of nodes, or species
\citep{costa2007characterization}--- the larger the algebraic connectivity, the more robust a
network is to cascading effects (e.g. Gaiarsa et al., submitted), and the harder it is to break the community into isolated groups of species.

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/robustness.pdf}
  \caption{The robustness of networks to species extinction and
    to cascading effects. The robustness to species extinction is measured by
    incrementally removing species by degree, through removing species
    by abundance did not yield qualitatively different results. The robustness of networks to cascading effects is measured as the algebraic connectivity, the second smallest eigenvalue of the Laplacian matrix. Points
    are the value for each site at each year of assembly. The solid
    line indicates the mean slope estimate and the dashed lines are
    the $95\%$ confidence intervals around the estimate.}
  \label{fig:rob}
\end{figure}
\clearpage

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible, even though two changing points did occur in the non assembling hedgerow six between 2009 and 2010, and 2010 and 2011 (HR6, Fig.~\ref{fig:changePoints}) . Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

Given that changing ponts did occur, TRANSITION... Surprisingly, the species that were most variable in
their network position and thus contributed most to network
reorganizations where species with the highest degrees (i.e., most
generalized) and persistence.  For example, the five most ubiquitous
species in our study landscape --- \textit{Halictus ligatus},
\textit{Halictus tripartitus},\textit{Lasioglossum (Dialictus)
  incompletum}, and \textit{Toxomerus marginatus} --- were also the
only species that changed what module (i.e., community) they were
present in across years in all of the assembling hedgerows. Because
species degree and persistence were strongly correlated, it is
difficult to disentangle the causal mechanism for why species with
those characteristics are so variable in their network
position. Generalized species may be best able to exploit the limited
floral resources the intensively managed agriculture landscape, and
thus also most persistent. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a higher degree. Either way, our result suggests
that adaptable species can change their network position to utilize
the most advantageous floral resources, which my depend the other
pollinator species that are present and the state of the floral
resource. Thus given the opportunity and ability to use different
resources, species will often change their network positions.
